---
title: "HW9"
author: "Cesar Dao (cad4837)"
date: "2024-04-18"
output: pdf_document
---
[Repository Link](https://github.com/cedaco/SDS315_HW9)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(mosaic)
library(tidyverse)
library(knitr)
library(MatchIt)
```

```{r, include = FALSE, echo = FALSE}
setwd("/Users/cesar/Desktop/SDS315")
turnout = read.csv("turnout.csv")
solder = read.csv("solder.csv")

```
# Part 1

## A
```{r, echo = FALSE}

mean(turnout$voted1998 == 1 & turnout$GOTV_call == 1)

mean(turnout$voted1998 == 1 & turnout$GOTV_call == 0)

diff_mean = do(10000) * diffmean(voted1998 == 1 ~ GOTV_call, data = mosaic::resample(turnout))

confint(diff_mean, level = 0.95)


```

## B
```{r, echo = FALSE}
ggplot(turnout) + geom_boxplot(aes(x = factor(GOTV_call), y = AGE)) 
ggplot(turnout) + geom_boxplot(aes(x = factor(voted1998), y = AGE)) 
ggplot(turnout) + geom_boxplot(aes(x = factor(voted1996), y = AGE)) 

```
Older people appear to have been more common targets for GOTV calls and appear to be more likely to have voted in the 1998 and 1996 elections.

```{r, echo = FALSE}
print("GOTV_call vs Major party affiliation ")
mean(MAJORPTY ~ GOTV_call, data=turnout)

print("If the person voted in 1998 vs Major party affiliation")
mean(MAJORPTY ~ voted1998, data=turnout)

print("If the person voted in 1996 vs  Major party affiliation")
mean(MAJORPTY ~ voted1996, data=turnout) 

```
These statistics show that those who are affiliated with a major party had slightly higher proportions of being subjects of GOTV_call, voting in 1998, and voting in 1996

## C
```{r, echo = FALSE}
match = matchit(GOTV_call ~ AGE + MAJORPTY + voted1996, data = turnout, ratio=5)
summary(match)
match = match.data(match)


```

```{r, echo = FALSE}
print("If the person received a GOTV_call vs if they voted or not in 1998")
prop(voted1998 ~ GOTV_call, data=match)
```

This new matched data appears to show that those that got a GOTV call had a higher proportion of people that voted than those who didnt get a GOTV call.

```{r}
diffmean_match= do(10000)*diffmean(voted1998 ~ GOTV_call, data=mosaic::resample(match))
confint(diffmean_match, level = 0.95)
lm_match = do(10000)*lm(voted1998 ~ GOTV_call, data=mosaic::resample(match))
confint(lm_match, level = 0.95)

```
I conclude that the GOTV call did not have a much of a relationship with whether someone voted or not since the estimate for the r squared statistic falls inside of its 95% confidence interval.

# Part 2

## A
```{r, echo = FALSE}
ggplot(solder) + geom_boxplot(aes(x = Opening, y = skips))
```
This plot shows that large openings appear to lead to the least amount of skips and that small openings seem to lead to a larger amount of skips. Medium openings appear to result in more skips than large openings but much less skips than small openings.

```{r, echo = FALSE}
ggplot(solder) + geom_boxplot(aes(x = Solder, y = skips))

```
This plot shows that thicker alloys seem to result in less skips and that thiner alloys seem to result in a larger amount of skips.

## B

```{r, echo = FALSE}
model = lm(skips ~ Opening, data = solder) 
confint(model, level = 0.95) %>% round(0)

model = lm(skips ~ Solder, data = solder) 
confint(model, level = 0.95) %>% round(0)

model = lm(skips ~ Opening:Solder, data = solder) 
confint(model, level = 0.95) %>% round(0)

```
## C

The differences in the estimates at 2.5% and 97.% for the 95% confidence interval appear to be practically significant for all the different variables being analyzed, as a even one skip could result in the failure of a circuit board. Some intervals contain negative numbers, which means that the given variable results in very miniscule amounts of skips/failure.

## D

Judging by the graphs and the intervals, I would recommend that the best combination of Opening size and alloy thickness would be a large sized opening and a thick alloy. These both appear to cause the least amount of skips and both together have the most negative confidence interval at 95% confidence.




